The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
hereafter

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.  Individual caribou (n = `r DT[, uniqueN(get(idcol))]`) are show as nodes and each indiviual is represented by a unique color. Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g. individual "A" in summer, forest and individual "A" in winter, forest).

@@

We modified the spatial distance threshold required for group assignment using
`spatsoc` [@Robitaille_2019] (see above) and re-assigned groups at incremental
distances between 5 - 500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group. We assumed these scales represented visual (short distance) to auditory (long distance) sensory modalities of caribou.

>>>>

(ref:ml) Visualization of multilayer network for social ungulate case study representing social association of caribou (*Rangifer tarandus*) on Fogo Island, Newfoundland in summer 2017 and winter 2018.  Individual caribou (n = `r DT[, uniqueN(get(idcol))]` females) are show as nodes and each indiviual is represented by a unique color. Six layers represent combinations of two seasons (summer and winter) and three habitat classes (open, forest and forage). Intralayer edges connect pairs of individuals that associated according to spatial and temporal thresholds described above, and are scaled in line thickness according to strength of association (SRI). Interlayer edges connect individuals to themselves across seasons and within habitat classes (e.g. individual "A" in summer, forest and individual "A" in winter, forest).

@@

We modified the distance threshold, hereafter the social threshold, required for group assignment using
`spatsoc` [@Robitaille_2019] and re-assigned groups at incremental
distances between 5 - 500 m. For example, at the finest social scale, only
individuals within 5 m of one another were considered in the same group, whereas
at the coarsest social scale, individuals within 500 m of one another were
considered in the same group. We assumed these scales represented visual (short distance) to auditory (long distance) sensory modalities of caribou.
